---
title: "Solutions"
author: "John Little"
date: "`r Sys.Date()`"
output: html_notebook
---


## Packages

As of this writing, visualizing sf object via ggplot2 requires the geom_sf() function, which is currently only available in the development version of ggplot2

```{}
devtools::install_github("tidyverse/ggplot2")
```


```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(sf)
library(tmap)
library(leaflet)
```

## Data

### Brazil Federal Protected Areas

i3Geo / Áreas Especiais / Unidades de Conservação / UCs federais de proteção integral
Special Areas > Conservation Units > Federal Procted Areas > click the download arrow

See Also:  http://mapas.mma.gov.br/geonetwork/srv/br/metadata.show?id=1250


### Brazil Country Boundary

- Brazil and other world shapefiles from http://Diva-GIS.org/gdata

Try to get a useful shapefile of Brazil, one with a funciton EGSP projection.   THEN, attach the patron's shapefile as a second layer, therby inheriting the proper projection and other GIS metadata.

So, http://www.diva-gis.org/datadown  and download Brazil

Initially I choose not to set the projection and that seems to work best for this project.  But the notation for assign projection is listed in the comment within the code chunk

```{r}
ucsfi <- read_sf("data/ucsfi.shp") #%>% 
#  `st_crs<-`(5527)  # 3857 is Web mercator
brazil0 <- read_sf("data/BRA_adm/BRA_adm0.shp")
```


## Projection

In the above code chunk projection is commented out because tmap appears to work beset **without** the projection assigned.  We'll do that later. assigned with `st_crs()` using a somewhat non-standard syntax. However, It seemed to be the only way I could add a projection to this particular shapefile.  Below are some other syntax examples that have worked for me with other shapefiles.  Of course there are various ways to add projection and since this is R, there's more than one way to accomplish the goal.

```{}
sf::st_crs(3857)
sf::st_transform(3857)
ggplot2::coord_sf(crs = 3857)   # must use the development version of ggplot2

```

### Notes on Projection

From [Brazillian CRS](https://wiki.osgeo.org/wiki/Brazilian_Coordinate_Reference_Systems)

- 4989 
- 4674
- 5527 -- SAD69 from 1995 onwards (SAD69 a partir de 1995)
- 4618 -- SAD69 before 1995 (SAD69 antes de 1995)
- 3857 -- 3857 is Web mercator


### Check Projection

```{r}
st_crs(ucsfi)
print("ucsfi above ^^^  --------- brazil0 below")
st_crs(brazil0)

# or check the projection for an individual polygon ...
# ucsfi$geometry %>% head(1) 
```

## First View With Projection

### Data Preview

```{r}
as_tibble(ucsfi)
```

### Wrangle Data

I want to use a numeric data type as my "fill"

```{r}
ucsfi <- ucsfi %>% 
  mutate(GID7 = as.numeric(GID7))
```


### First Look with tmap

```{r}
tmap_mode("plot")

tm_shape(brazil0, projection = 3857) + tm_fill() + tm_text("NAME_0", auto.placement = FALSE) +
  tm_shape(ucsfi, projection = 3857) + tm_fill("GID7", palette = rev(sf.colors()))
```


### ggplot

```{r}
ucsfi %>% 
  mutate(ANO_CRIA6 = as.numeric(ANO_CRIA6)) %>% 
  ggplot() +
  geom_sf(aes(fill = ANO_CRIA6, color = ANO_CRIA6)) 
```


### Look 3 -- Leaflet

```{r}
MapPalette <- colorQuantile(palette = "viridis", domain = ucsfi$GID7, n = 7, reverse = TRUE)
```


```{r}
ucsfi %>% 
  leaflet(width = "100%") %>% 
  addProviderTiles( provider = "CartoDB.Positron") %>% 
  addPolygons(popup = ~ ID_UC0,
              stroke = FALSE,
              smoothFactor = 0,
              fillOpacity = 0.7,
              color = ~ MapPalette(GID7)) 
#+
#  addLegend("bottomright", 
#              pal = MapPalette, 
#              values = ~ GID7,
#              title = "GID7",
#              opacity = 1)
```
 

