---
title: "Intersect & Area"
author: "John Little"
date: "`R Sys.Date()`"
output: html_notebook
---

## Questions

4. calculate **area** of obtained polygons 
3. **intersect** with an existing shapefile. 

## Packages

```{r}
library(tidyverse)
library(sf)
```


## Load Data

```{r}
ucsfi <- read_sf("data/ucsfi.shp")  # %>% `st_crs<-`(5527)  
brazil0 <- read_sf("data/BRA_adm/BRA_adm0.shp")
```

## Harmonize CRS

```{r}
ucsfi <- ucsfi %>% `st_crs<-`(4326)
```

## Area

- **Requires** `library(lwgeom)`
- Units reported in meters squared

```{r}
st_area(brazil0)

ucsfi %>% 
  head() %>% 
  select(geometry) %>% 
  st_area()
```

## Intersect

- `st_intersects`   -- Logical
- `st_intersection`  -- Gives the Object that is intersection
- `?st_intersects`  -- getting help

**Note**:  getting help on st_intrsects will reveal a whole host of useful functions:  disjoint, touches, crosses, within, etc.


```{r}
st_intersects(brazil0, ucsfi$geometry[1])
st_intersects(ucsfi$geometry[1], brazil0)
```

```{r}
what1 <- st_intersection(ucsfi$geometry[1], brazil0)
what2 <- st_intersection(brazil0, ucsfi$geometry[1])

what1
what2

```



```{r}
class(what1)
class(what2)
```


```{r}
ggplot() +
  geom_sf(aes(), data = what2)
```

```{r}
Nucsfi %>% 
  head(1) %>% 
  ggplot() +
  geom_sf(aes())

```

